Local PCA Shows How the Effect of Population Structure Differs Along the Genome

### 2018-08-08 writeup/local_pca_paper.tex
fixed up latex

\newif\ifsubmission
\submissiontrue
% \submissionfalse
\ifsubmission
    % % stuff for submission
    \usepackage[nofiglist,nomarkers,figuresonly]{endfloat}
    \usepackage{setspace}
    % \doublespacing
    \bibliographystyle{plos2015}
    \newcommand\citet{\cite}
    \newcommand\citep{\cite}
    \renewcommand\includegraphics{\relax}
    \renewcommand{\includegraphics}[2][]{\relax}
    \renewcommand{\figurename}{Fig.}
    \newcommand{\Figure}{Fig }
    \newcommand{\Figures}{Fig }
\else
    % for the nice version
    \usepackage[square,sort,comma,numbers]{natbib} \bibpunct{(}{)}{;}{author-year}{}{,} 
    \bibliographystyle{plainnat}
    \newcommand{\Figure}{{Figure }}
    \newcommand{\Figures}{{Figures }}
    \renewcommand{\linelabel}[1]{}
\fi
% grrr
\newcommand{\citetx}[2][]{\ifsubmission#1 \cite{#2}\else\citet{#2}\fi}

@@

\begin{figure}
    \begin{center}
        \ifusepngs
            \includegraphics{MDS_allchr_Together_plot_samples_noinv.png}
        \else
            \includegraphics{MDS_allchr_Together_plot_samples_noinv}
        \fi
    \end{center}
    \caption{
        Variation in structure for windows of 1,000 SNPs 
        across \textit{Drosophila melanogaster} chromosome arms: without inversions.
         As in \Figure \ref{fig:mds_allchr}, but after omitting for each chromosome arm individuals carrying the less frequent orientation
         of any inversions on that chromosome arm.
         The values differ from those in \ref{fig:drosophila_recomb_rate}
         in the window size used and that some MDS values were inverted
         (but relative orientation is meaningless as chromosome arms were run separately,
         unlike for \textit{Medicago}).
        In all plots, each point represents one window along the genome.
         The first column shows the MDS visualization of relationships between windows, 
         and the second and third columns show the midpoint of each window against the two MDS coordinates; 
         rows correspond to chromosome arms.
         Colors are consistent for plots in each row. 
         Vertical lines show the breakpoints of known polymorphic inversions.   
         \label{sfig:mds_allchr_noinversions}
    }
\end{figure}

@@

\begin{figure}
    \begin{center}
       \includegraphics[width=0.82\textwidth]{FigS_plot_corners-1_run_012720}
    \end{center}
    \caption{
        MDS visualizations of simulation run_012720 (RECOMBTYPE, ``step"; SELTYPE, ``neutral")
        \label{sfig:mds_run_012720}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics[width=0.82\textwidth]{FigS_plot_corners-1_run_027034}
    \end{center}
    \caption{
        MDS visualizations of simulation run_027034 (RECOMBTYPE, ``base"; SELTYPE, ``neutral")
        \label{sfig:mds_run_027034}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics[width=0.82\textwidth]{FigS_plot_corners-1_run_015598}
    \end{center}
    \caption{
        MDS visualizations of simulation run_015598 (RECOMBTYPE, ``hotspot"; SELTYPE, ``neutral")
        \label{sfig:mds_run_015598}
    }
\end{figure}

@@

\begin{figure}
    \begin{center}
       \includegraphics[width=0.82\textwidth]{FigS_plot_corners-1_run_005464}
    \end{center}
    \caption{
        MDS visualizations of simulation run_005464 (RECOMBTYPE, ``base"; SELTYPE, ``selected")
        \label{sfig:mds_run_005464}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics[width=0.82\textwidth]{FigS_plot_corners-1_run_031486}
    \end{center}
    \caption{
        MDS visualizations of simulation run_031486 (RECOMBTYPE, ``base"; SELTYPE, ``selected")
        \label{sfig:mds_run_031486}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics[width=0.82\textwidth]{FigS_plot_corners-1_run_009673}
    \end{center}
    \caption{
        MDS visualizations of simulation run_009673 (RECOMBTYPE, ``step"; SELTYPE, ``selected")
        \label{sfig:mds_run_009673}
    }
\end{figure}

>>>>

\newif\ifsubmission
% \submissiontrue
\submissionfalse
\ifsubmission
    % % stuff for submission
    \usepackage[nofiglist,nomarkers,figuresonly]{endfloat}
    \usepackage{setspace}
    % \doublespacing
    \bibliographystyle{plos2015}
    \newcommand\citet{\cite}
    \newcommand\citep{\cite}
    \renewcommand\includegraphics{\relax}
    \renewcommand{\includegraphics}[2][]{\relax}
    \renewcommand{\figurename}{Fig.}
    \newcommand{\Figure}{Fig }
    \newcommand{\Figures}{Fig }
\else
    % for the nice version
    \usepackage[square,sort,comma,numbers]{natbib} \bibpunct{(}{)}{;}{author-year}{}{,} 
    \bibliographystyle{plainnat}
    \newcommand{\Figure}{{Figure }}
    \newcommand{\Figures}{{Figures }}
    \renewcommand{\linelabel}[1]{}
\fi
% grrr
\newcommand{\citetx}[2][]{\ifsubmission#1 \cite{#2}\else\citet{#2}\fi}

@@

\begin{figure}
    \begin{center}
        \ifusepngs
            \includegraphics[width=\textwidth]{MDS_allchr_Together_plot_samples_noinv.png}
        \else
            \includegraphics[width=\textwidth]{MDS_allchr_Together_plot_samples_noinv}
        \fi
    \end{center}
    \caption{
        Variation in structure for windows of 1,000 SNPs 
        across \textit{Drosophila melanogaster} chromosome arms: without inversions.
         As in \Figure \ref{fig:mds_allchr}, but after omitting for each chromosome arm individuals carrying the less frequent orientation
         of any inversions on that chromosome arm.
         The values differ from those in \ref{fig:drosophila_recomb_rate}
         in the window size used and that some MDS values were inverted
         (but relative orientation is meaningless as chromosome arms were run separately,
         unlike for \textit{Medicago}).
        In all plots, each point represents one window along the genome.
         The first column shows the MDS visualization of relationships between windows, 
         and the second and third columns show the midpoint of each window against the two MDS coordinates; 
         rows correspond to chromosome arms.
         Colors are consistent for plots in each row. 
         Vertical lines show the breakpoints of known polymorphic inversions.   
         \label{sfig:mds_allchr_noinversions}
    }
\end{figure}

@@

\begin{figure}
    \begin{center}
       \includegraphics[width=0.82\textwidth]{FigS_plot_corners-1_run_012720}
    \end{center}
    \caption{
        MDS visualizations of simulation run 012720 (RECOMBTYPE, ``step"; SELTYPE, ``neutral")
        \label{sfig:mds_run_012720}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics[width=0.82\textwidth]{FigS_plot_corners-1_run_027034}
    \end{center}
    \caption{
        MDS visualizations of simulation run 027034 (RECOMBTYPE, ``base"; SELTYPE, ``neutral")
        \label{sfig:mds_run_027034}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics[width=0.82\textwidth]{FigS_plot_corners-1_run_015598}
    \end{center}
    \caption{
        MDS visualizations of simulation run 015598 (RECOMBTYPE, ``hotspot"; SELTYPE, ``neutral")
        \label{sfig:mds_run_015598}
    }
\end{figure}

@@

\begin{figure}
    \begin{center}
       \includegraphics[width=0.82\textwidth]{FigS_plot_corners-1_run_005464}
    \end{center}
    \caption{
        MDS visualizations of simulation run 005464 (RECOMBTYPE, ``base"; SELTYPE, ``selected")
        \label{sfig:mds_run_005464}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics[width=0.82\textwidth]{FigS_plot_corners-1_run_031486}
    \end{center}
    \caption{
        MDS visualizations of simulation run 031486 (RECOMBTYPE, ``base"; SELTYPE, ``selected")
        \label{sfig:mds_run_031486}
    }
\end{figure}

\begin{figure}
    \begin{center}
       \includegraphics[width=0.82\textwidth]{FigS_plot_corners-1_run_009673}
    \end{center}
    \caption{
        MDS visualizations of simulation run 009673 (RECOMBTYPE, ``step"; SELTYPE, ``selected")
        \label{sfig:mds_run_009673}
    }
\end{figure}
